Price of Anarchy for Mean Field Games

### 2018-07-22 PoA.tex
proofreading Proposition 7

	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$. From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t>0.$$
	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By the assumption on $\lambda$, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}>0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

@@

    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq (q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}
    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. It is easy to check that $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.

>>>>

	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$. From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By our assumption on $\bar{b}_1$, we have $A^{u,b_1\to 0} \neq A^{w,b_1\to 0}$ and thus, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

@@

    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}
    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. It is easy to check that $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
